---
title: "Project 3 Knit"
author: "Nathan Riojas, Ryan Billa, Corey monreal-Jackson"
date: "October 10, 2015"
output: html_document
---

#### Steps used to create this project
#####1. Using GitHub, create a Repo
#####2. Clone the Repository into the Data Visualization Folder (Or the folder you wish)
#####3. Create R Studio Folders for all the project development (folder descriptions below)
#####4. Find several CSVs that are in the business and financial sector.
#####5. Modify the R_ETL.R given and run the code to get the code to develop a SQL table
#####6. Using Oracle SQL Developer, paste the code output from the R_ETL.R script to create a table
#####7. After the table is created, import the data from the CSV reformattted file to the table
#####8. Use a query statement similar to the TitanicAnalysis.R file (used in the last project) to build a data frame with the CSV data from Oracle 
#####9. Build 3 different workflows using R code and %>%. These will become new dataframes. An inner join, outer join and one other join will be used.
#####10. Generate unique plots from the workflow dataframes
#####11. Call these files in a .Rmd file using the R markdown command "source" and press Knit HTML to view the data/plots. (Code seen below) Note: Tables will also be generated to show the what the workflows created.


#### Folders Needed
#####00 Doc: Holds the .Rmd and .html files containing these instructions and project output. Also holds RPROFILE to load all required packages.
#####01 Data: Generates the code to create the table in Oracle. Gathers the data from the database for and puts it into data frames
#####02 Data Wrangling: Contains the .R files that use create workflows from the data frame create from the CSV data put into Oracle.
#####03 Visualization: Contains the .R files that use ggplot to generate graph our graphs


#### R markdown code
#####Immediately below is the code we adjusted from the R_ETL.R File. Its is directly pasted from the code because in the code it calls the csv so it cannot run if sourced.
#####The .R file is called using the command directly after. The subsequent code/graphs illustrates the code that goes into


'''
require(tidyr)
require(dplyr)
require(ggplot2)


setwd("C:/Users/Nathan R/Documents/DataVisualization/Project 3/01 Data/CSV_Files")

file_path <- "Country_Pop_1980_2010.csv"

df <- read.csv(file_path, stringsAsFactors = FALSE)

#Replace "." (i.e., period) with "_" in the column names.
names(df) <- gsub("\\.+", "_", names(df))

str(df) # Uncomment this and  run just the lines to here to get column types to use for getting the list of measures.

measures <- c("Year")
#measures <- NA # Do this if there are no measures.

#Get rid of special characters in each column.
#Google ASCII Table to understand the following:
for(n in names(df)) {
 df[n] <- data.frame(lapply(df[n], gsub, pattern="[^ -~]",replacement= ""))
}

dimensions <- setdiff(names(df), measures)
if( length(measures) > 1 || ! is.na(dimensions)) {
  for(d in dimensions) {
    # Get rid of " and ' in dimensions.
    df[d] <- data.frame(lapply(df[d], gsub, pattern="[\"']",replacement= ""))
    # Change & to and in dimensions.
    df[d] <- data.frame(lapply(df[d], gsub, pattern="&",replacement= " and "))
    # Change : to ; in dimensions.
    df[d] <- data.frame(lapply(df[d], gsub, pattern=":",replacement= ";"))
  }
}

library(lubridate)
#Fix date columns, this needs to be done by hand because | needs to be correct.
#                                                      \_/


#The following is an example of dealing with special cases like making state abbreviations be all upper case.
#df["State"] <- data.frame(lapply(df["State"], toupper))

#Get rid of all characters in measures except for numbers, the - sign, and period.dimensions
if( length(measures) > 1 || ! is.na(measures)) {
  for(m in measures) {
    df[m] <- data.frame(lapply(df[m], gsub, pattern="[^--.0-9]",replacement= ""))
  }
}

write.csv(df, paste(gsub(".csv", "", file_path), ".reformatted.csv", sep=""), row.names=FALSE, na = "")

tableName <- gsub(" +", "_", gsub("[^A-z, 0-9, ]", "", gsub(".csv", "", file_path)))
sql <- paste("CREATE TABLE", tableName, "(\n-- Change table_name to the table name you want.\n")
if( length(measures) > 1 || ! is.na(dimensions)) {
  for(d in dimensions) {
    sql <- paste(sql, paste(d, "varchar2(4000),\n"))
  }
}
if( length(measures) > 1 || ! is.na(measures)) {
  for(m in measures) {
    if(m != tail(measures, n=1)) sql <- paste(sql, paste(m, "number(38,4),\n"))
    else sql <- paste(sql, paste(m, "number(38,4)\n"))
  }
}
sql <- paste(sql, ");")
cat(sql)
'''



'''require(tidyr)
require(dplyr)
require(ggplot2)

setwd("C:/Users/Nathan R/Documents/DataVisualization/Project 3/01 Data/CSV_Files")

file_path <- "Dow Jones Industrial Average.csv"

df <- read.csv(file_path, stringsAsFactors = FALSE)

#Replace "." (i.e., period) with "_" in the column names.
names(df) <- gsub("\\.+", "_", names(df))

str(df) # Uncomment this and  run just the lines to here to get column types to use for getting the list of measures.

measures <- c("Year", "Open_",	"High",	"Low",	"Close_",	"Volume",	"Adj_Close
")
#measures <- NA # Do this if there are no measures.

#Get rid of special characters in each column.
#Google ASCII Table to understand the following:
for(n in names(df)) {
  df[n] <- data.frame(lapply(df[n], gsub, pattern="[^ -~]",replacement= ""))
}

dimensions <- setdiff(names(df), measures)
if( length(measures) > 1 || ! is.na(dimensions)) {
  for(d in dimensions) {
    # Get rid of " and ' in dimensions.
    df[d] <- data.frame(lapply(df[d], gsub, pattern="[\"']",replacement= ""))
    # Change & to and in dimensions.
    df[d] <- data.frame(lapply(df[d], gsub, pattern="&",replacement= " and "))
    # Change : to ; in dimensions.
    df[d] <- data.frame(lapply(df[d], gsub, pattern=":",replacement= ";"))
  }
}

library(lubridate)
#Fix date columns, this needs to be done by hand because | needs to be correct.
#                                                      \_/
df$Date <- gsub(" [0-9]+:.*", "", gsub(" UTC", "", mdy(as.character(df$Date), tz="UTC")))

#The following is an example of dealing with special cases like making state abbreviations be all upper case.
df["State"] <- data.frame(lapply(df["State"], toupper))

#Get rid of all characters in measures except for numbers, the - sign, and period.dimensions
if( length(measures) > 1 || ! is.na(measures)) {
  for(m in measures) {
    df[m] <- data.frame(lapply(df[m], gsub, pattern="[^--.0-9]",replacement= ""))
  }
}

write.csv(df, paste(gsub(".csv", "", file_path), ".reformatted.csv", sep=""), row.names=FALSE, na = "")

tableName <- gsub(" +", "_", gsub("[^A-z, 0-9, ]", "", gsub(".csv", "", file_path)))
sql <- paste("CREATE TABLE", tableName, "(\n-- Change table_name to the table name you want.\n")
if( length(measures) > 1 || ! is.na(dimensions)) {
  for(d in dimensions) {
    sql <- paste(sql, paste(d, "varchar2(4000),\n"))
  }
}
if( length(measures) > 1 || ! is.na(measures)) {
  for(m in measures) {
    if(m != tail(measures, n=1)) sql <- paste(sql, paste(m, "number(38,4),\n"))
    else sql <- paste(sql, paste(m, "number(38,4)\n"))
  }
}
sql <- paste(sql, ");")
cat(sql)
'''


'''setwd("C:/Users/Nathan R/Documents/DataVisualization/Project 3/01 Data")

file_path <- "Fortune 500 Companies.csv"

df <- read.csv(file_path, stringsAsFactors = FALSE)

#Replace "." (i.e., period) with "_" in the column names.
names(df) <- gsub("\\.+", "_", names(df))

#str(df) # Uncomment this and  run just the lines to here to get column types to use for getting the list of measures.

measures <- c("Year", "Rank")
#measures <- NA # Do this if there are no measures.

#Get rid of special characters in each column.
#Google ASCII Table to understand the following:
for(n in names(df)) {
  df[n] <- data.frame(lapply(df[n], gsub, pattern="[^ -~]",replacement= ""))
}

dimensions <- setdiff(names(df), measures)
if( length(measures) > 1 || ! is.na(dimensions)) {
  for(d in dimensions) {
    # Get rid of " and ' in dimensions.
    df[d] <- data.frame(lapply(df[d], gsub, pattern="[\"']",replacement= ""))
    # Change & to and in dimensions.
    df[d] <- data.frame(lapply(df[d], gsub, pattern="&",replacement= " and "))
    # Change : to ; in dimensions.
    df[d] <- data.frame(lapply(df[d], gsub, pattern=":",replacement= ";"))
  }
}

library(lubridate)
#Fix date columns, this needs to be done by hand because | needs to be correct.
#                                                      \_/


#The following is an example of dealing with special cases like making state abbreviations be all upper case.
df["State"] <- data.frame(lapply(df["State"], toupper))

#Get rid of all characters in measures except for numbers, the - sign, and period.dimensions
if( length(measures) > 1 || ! is.na(measures)) {
  for(m in measures) {
    df[m] <- data.frame(lapply(df[m], gsub, pattern="[^--.0-9]",replacement= ""))
  }
}

write.csv(df, paste(gsub(".csv", "", file_path), ".reformatted.csv", sep=""), row.names=FALSE, na = "")

tableName <- gsub(" +", "_", gsub("[^A-z, 0-9, ]", "", gsub(".csv", "", file_path)))
sql <- paste("CREATE TABLE", tableName, "(\n-- Change table_name to the table name you want.\n")
if( length(measures) > 1 || ! is.na(dimensions)) {
  for(d in dimensions) {
    sql <- paste(sql, paste(d, "varchar2(4000),\n"))
  }
}
if( length(measures) > 1 || ! is.na(measures)) {
  for(m in measures) {
    if(m != tail(measures, n=1)) sql <- paste(sql, paste(m, "number(38,4),\n"))
    else sql <- paste(sql, paste(m, "number(38,4)\n"))
  }
}
sql <- paste(sql, ");")
cat(sql)
'''



'''require(tidyr)
require(dplyr)
require(ggplot2)

setwd("C:/Users/Nathan R/Documents/DataVisualization/Project 3/01 Data/CSV_Files")

file_path <- "Oil & Gas 1985-2000.csv"

df <- read.csv(file_path, stringsAsFactors = FALSE)

#Replace "." (i.e., period) with "_" in the column names.
names(df) <- gsub("\\.+", "_", names(df))

str(df) # Uncomment this and  run just the lines to here to get column types to use for getting the list of measures.

measures <- c("Months in Production",	"Gas Produced, MCF",	"Water Produced, bbl",	"Reporting Year")
#measures <- NA # Do this if there are no measures.

#Get rid of special characters in each column.
#Google ASCII Table to understand the following:
for(n in names(df)) {
  df[n] <- data.frame(lapply(df[n], gsub, pattern="[^ -~]",replacement= ""))
}

dimensions <- setdiff(names(df), measures)
if( length(measures) > 1 || ! is.na(dimensions)) {
  for(d in dimensions) {
    # Get rid of " and ' in dimensions.
    df[d] <- data.frame(lapply(df[d], gsub, pattern="[\"']",replacement= ""))
    # Change & to and in dimensions.
    df[d] <- data.frame(lapply(df[d], gsub, pattern="&",replacement= " and "))
    # Change : to ; in dimensions.
    df[d] <- data.frame(lapply(df[d], gsub, pattern=":",replacement= ";"))
  }
}

library(lubridate)

#The following is an example of dealing with special cases like making state abbreviations be all upper case.
df["State"] <- data.frame(lapply(df["State"], toupper))

#Get rid of all characters in measures except for numbers, the - sign, and period.dimensions
if( length(measures) > 1 || ! is.na(measures)) {
  for(m in measures) {
    df[m] <- data.frame(lapply(df[m], gsub, pattern="[^--.0-9]",replacement= ""))
  }
}

write.csv(df, paste(gsub(".csv", "", file_path), ".reformatted.csv", sep=""), row.names=FALSE, na = "")

tableName <- gsub(" +", "_", gsub("[^A-z, 0-9, ]", "", gsub(".csv", "", file_path)))
sql <- paste("CREATE TABLE", tableName, "(\n-- Change table_name to the table name you want.\n")
if( length(measures) > 1 || ! is.na(dimensions)) {
  for(d in dimensions) {
    sql <- paste(sql, paste(d, "varchar2(4000),\n"))
  }
}
if( length(measures) > 1 || ! is.na(measures)) {
  for(m in measures) {
    if(m != tail(measures, n=1)) sql <- paste(sql, paste(m, "number(38,4),\n"))
    else sql <- paste(sql, paste(m, "number(38,4)\n"))
  }
}
sql <- paste(sql, ");")
cat(sql)
'''












```{r warning = FALSE}
source("../00 Doc/RPROFILE.R", echo = TRUE)
source("../01 Data/Business_DataFrames.R", echo = TRUE)
source("../02 Data Wrangling/Business Wrangling.R", echo = TRUE)
source("../03 Visualizations/Business_Visualizations.R", echo = TRUE)
```{r}